\textbf{Dynamic Hover Detection:\\Creating GUIs in Elm}

### 2013-12-15 paper/paper.tex
Add citations

Elm was introduced in March 2012 in Evan Czaplicki's senior thesis,
\emph{Concurrent FRP for GUIs}. He and his adviser, Stephen Chong,
published \emph{Asynchronous FRP for GUIs} at PLDI 2013. Both papers are
comprehensive overviews of Elm, and additionally provide excellent
literature reviews of previous FRP GUI endeavors, of which there are
several. Elm compiles down to JavaScript to run in the browser, making
it remarkably portable.

@@

There are two features of Elm we are deliberately avoiding. First is the
extensive raster drawing library, \texttt{Graphics.Collage}. Dynamic
hover detection is not problematic when using this library because it
can be done purely through manual collision detection. However, if we
used this library, our GUI would be a single raster animation and not a
DOM tree. Secondly, the \texttt{Graphics.Input} library contains
wrappers around HTML checkboxes and dropdowns. We consider creating GUIs
with these to be uninteresting and wanted to pursue something more
general. This led to the choice of an interface typically found in the
operating system rather than the browser. We do refer to the native GUI
constructs to show how the technique we develop for hovering
generalizes, as the API for buttons and hover detection is very similar.

@@

\begin{quote}
The type system rules out programs that use signals of signals, for the
following reason. Intuitively, if we have signals of signals, then after
a program has executed for, say 10 minutes, we might create a signal
that (through the use of \texttt{foldp}) depends on the history of an
input signal, say \texttt{Window.width}.
\end{quote}

@@

\begin{quote}
To compute the current value of this signal, should we use the entire
history of \texttt{Window.width}? But that would require saving all
history of \texttt{Window.width} from the beginning of execution, even
though we do not know whether the history will be needed later.
Alternatively, we could compute the current value of the signal just
using the current and new values of \texttt{Window.width} (i.e.,
ignoring the history). But this would allow the possibility of having
two identically defined signals that have different values, based on
when they were created. We avoid these issues by ruling out signals of
signals.
\end{quote}

@@

Notice the similarity with \texttt{hoverables}. Each call of
\texttt{customButton} provides the identifier event when the button is
clicked, and three (pure) Elements to display: one normally, one on
hover, and one on click. The result is an \texttt{Element}, not a
\texttt{Signal Element}, that nevertheless changes among those three in
response to the mouse. This is possible because the result Element's
dimensions are taken to be the maximum of the three inputs' dimensions.
Even if the Elements have different sizes, the resulting element and
therefore the hover surface remains fixed in size. Although the same
join technique can be applied, we find it likely that it would not work
as intended.
%Note to Max: I think it does work...

@@

\subsection{Acknowledgments}\label{acknowledgments}

We would like to thank Evan Czaplicki and Stephen Chong for creating
Elm, and the Elm community for growing it. We thank Norman Ramsey for
his guidance through functional programming, and our paper reviewers,
\ldots{} .

\subsection{References}\label{references}
%Make sure to put a link to our GitHub

\end{document}

>>>>

Elm was introduced in March 2012 in Evan Czaplicki's senior thesis,
\emph{Concurrent FRP for GUIs}. \cite{elm-thesis} He and his adviser, Stephen
Chong, published \emph{Asynchronous FRP for GUIs} at PLDI
2013. \cite{CzaplickiC13} Both papers are comprehensive overviews of Elm, and
additionally provide excellent literature reviews of previous FRP GUI endeavors,
of which there are several.  Elm compiles down to JavaScript to run in the
browser, making it remarkably portable.

@@

There are two features of Elm we are deliberately avoiding. First is the
extensive raster drawing library, \texttt{Graphics.Collage}. Dynamic hover
detection is not problematic when using this library because it can be done
purely through manual collision detection. However, if we used this library, our
GUI would be a single raster animation and not a DOM tree. Secondly, the
\texttt{Graphics.Input} library contains wrappers around HTML checkboxes and
dropdowns. We rejected creating GUIs with these and wanted to pursue something
more general. This led to the choice of an interface typically found in the
operating system rather than the browser. We do refer to the native GUI
constructs to show how the technique we develop for hovering generalizes, as the
API for buttons and hover detection is very similar.

@@

\begin{quote}
The type system rules out programs that use signals of signals, for the
following reason. Intuitively, if we have signals of signals, then after
a program has executed for, say 10 minutes, we might create a signal
that (through the use of \texttt{foldp}) depends on the history of an
input signal, say \texttt{Window.width}. \cite{CzaplickiC13}
\end{quote}

@@

\begin{quote}
To compute the current value of this signal, should we use the entire
history of \texttt{Window.width}? But that would require saving all
history of \texttt{Window.width} from the beginning of execution, even
though we do not know whether the history will be needed later.
Alternatively, we could compute the current value of the signal just
using the current and new values of \texttt{Window.width} (i.e.,
ignoring the history). But this would allow the possibility of having
two identically defined signals that have different values, based on
when they were created. We avoid these issues by ruling out signals of
signals. \cite{CzaplickiC13}
\end{quote}

@@

Notice the similarity with \texttt{hoverables}. Each call of
\texttt{customButton} provides the identifier event when the button is
clicked, and three (pure) Elements to display: one normally, one on
hover, and one on click. The result is an \texttt{Element}, not a
\texttt{Signal Element}, that nevertheless changes among those three in
response to the mouse. This is possible because the result Element's
dimensions are taken to be the maximum of the three inputs' dimensions.
Even if the Elements have different sizes, the resulting Element and
therefore the hover surface remains fixed in size. Although the same
join technique can be applied, we find it likely that it would not work
as intended.
%Note to Max: I think it does work...
%We should try it out then.

@@

\section*{Acknowledgments}
We would like to thank Evan Czaplicki and Stephen Chong for creating
Elm, and the Elm community for growing it. We thank Norman Ramsey for
his guidance through functional programming, and our paper reviewers,
\ldots{} .

%Make sure to put a link to our GitHub
\bibliographystyle{alpha}
\bibliography{refs.bib}
\end{document}
